An Evolutionary Algorithm for the Multiobjective Risk-Equity Constrained Routing Problem

### 2011-11-30 DAW_hazmatHypE/tags/submittedToDAM/paper/submissionDAM/hazmatRouting_EvolOptim.tex
renamed misspelled subfolder

\begin{figure}%
\includegraphics[width=\columnwidth]{figs/truckpaths}%
\caption{\label{fig:paths} Illustration of the variable-length representation of a solution (left) with its two paths for commodity 1 and one path for commodity 2 in opposition to the resulting full source--destination paths where the last part is the shortest path between the variable-length path's end node and the destination node for this commodity (right). The source and destination nodes for commodity 1 are 0 and 6 and for the second commodity the source is node 1 and the destination is node 7. The smaller numbers along the arcs of the graph in the middle depict the costs of the instance.}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.48\columnwidth]{figs/correlationLazio41.eps}
	\hfill
	\includegraphics[width=0.48\columnwidth]{figs/correlationUncorrelated4.eps}
	\caption{\label{fig:correlation} Correlation between the costs and the risks of the first commodity for both the lazio\_4\_1 instance (left) and the uncorrelated\_4 instance (right). A single point corresponds to a single arc.}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.75\columnwidth]{../experiments/randVsCost/compAll_2000gens.eps}
	\caption{\label{fig:compareAll} Comparison between the different instances lazio\_2 (squares), lazio\_3 (circles), lazio\_4\_1 (diamonds), lazio\_4\_2 (crosses), and lazio\_4\_3 (stars). Shown are the non-dominated solutions in the final populations of 10 independent HypE runs with population size 50 after 2000 generations.}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.48\columnwidth]{../experiments/randVsCost/hypervolumes/hypervolumeOverTime_50.eps}
	\hfill
	\includegraphics[width=0.48\columnwidth]{../experiments/randVsCost/hypervolumes/hypervolumeOverTime_100.eps}
	\caption{\label{fig:hypervolumeOverTime} Boxplots of hypervolume values over time for numbers of generations in $[250, \ldots, 2000]$ for HypE with population size 50 (left) and population size 100 (right) on the lazio\_4 instance.}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.75\columnwidth]{../experiments/randVsCost/randVsCost_ns4_1_OriginalCost_2000gens.eps}
	\vspace{-1em}
	\caption{\label{fig:randVsCostOriginal} Comparison between the random initialization ($\circ$) and the cost-optimal one ($\times$). Shown are the non-dominated solutions in the final populations of 10 independent HypE runs with population size 50 after 2000 generations for all three objectives (top left) and each combination of two objectives on the lazio\_4\_1 instance.}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.75\columnwidth]{../experiments/randVsCost/randVsCost_ns4_1_New_2000gens.eps}
	\vspace{-1em}
	\caption{\label{fig:randVsCostNew} Comparison between the random initialization ($\circ$) and the cost-optimal one ($\times$). Shown are the non-dominated solutions in the final populations of 10 independent HypE runs with population size 50 after 2000 generations on the uncorrelated\_4 instance.}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.48\columnwidth]{../experiments/randVsCost/hypervolumes/initBoxPlots_OriginalCosts.eps}
	\hfill
	\includegraphics[width=0.48\columnwidth]{../experiments/randVsCost/hypervolumes/initBoxPlots_New.eps}
	\vspace{-1em}
	\caption{\label{fig:costVsRandBoxPlots} Comparison between the random initialization and the cost-optimal one.
	Shown are boxplots of hypervolume values for HypE with population size 50 on the lazio\_4 instance (left) and on the uncorrelated\_4 instance (right) after both 250 and 2000 generations.}
\end{figure}

@@

\begin{figure}%
	\centering
	\includegraphics[width=0.75\columnwidth]{../experiments/randVsCost/diffPopsizes}%
	\vspace{-1em}
	\caption{\label{fig:popsizes} Nondominated solutions of 10 independent runs after 100,000 function evaluations for HypE with a population size of 50 ($\times$), 100 ($\circ$), and 200 ($\square$) respectively.}
\end{figure}

\begin{figure}%
	\centering
	\includegraphics[width=0.5\columnwidth]{../experiments/randVsCost/hypervolumes/algoComparison}%
	\caption{\label{fig:algoComparison} Boxplots of the hypervolume values of 10 independent runs after 100,000 function evaluations of HypE with a population size of 25, 50, 100, and 200, as well as for NSGA-II.}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.75\columnwidth]{../experiments/randVsCost/WHypEVsHypE_ns4_1_OriginalCosts2.eps}
	\vspace{-1em}
	\caption{\label{fig:whype} Comparison between the standard HypE selection ($\circ$) with the one of W-HypE ($\times$) when the weighted hypervolume indicator is only sampled in the gray shaded box $[7\cdot 10^3, 10^4]\times[3\cdot 10^7, 4\cdot 10^7]\times[5\cdot 10^5, 1.1\cdot 10^6]$. Shown are all non-dominated solutions for each algorithm after 10 runs with 4,000 generations and population size 25.}
\end{figure}

@@

% 
 \bibliographystyle{plainnat}
 \footnotesize
 \bibliography{all}

>>>>

\begin{figure}%
\includegraphics[width=\columnwidth]{truckpaths}%
\caption{\label{fig:paths} Illustration of the variable-length representation of a solution (left) with its two paths for commodity 1 and one path for commodity 2 in opposition to the resulting full source--destination paths where the last part is the shortest path between the variable-length path's end node and the destination node for this commodity (right). The source and destination nodes for commodity 1 are 0 and 6 and for the second commodity the source is node 1 and the destination is node 7. The smaller numbers along the arcs of the graph in the middle depict the costs of the instance.}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.48\columnwidth]{correlationLazio41.eps}
	\hfill
	\includegraphics[width=0.48\columnwidth]{correlationUncorrelated4.eps}
	\caption{\label{fig:correlation} Correlation between the costs and the risks of the first commodity for both the lazio\_4\_1 instance (left) and the uncorrelated\_4 instance (right). A single point corresponds to a single arc.}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.75\columnwidth]{compAll_2000gens.eps}
	\caption{\label{fig:compareAll} Comparison between the different instances lazio\_2 (squares), lazio\_3 (circles), lazio\_4\_1 (diamonds), lazio\_4\_2 (crosses), and lazio\_4\_3 (stars). Shown are the non-dominated solutions in the final populations of 10 independent HypE runs with population size 50 after 2000 generations.}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.48\columnwidth]{hypervolumeOverTime_50.eps}
	\hfill
	\includegraphics[width=0.48\columnwidth]{hypervolumeOverTime_100.eps}
	\caption{\label{fig:hypervolumeOverTime} Boxplots of hypervolume values over time for numbers of generations in $[250, \ldots, 2000]$ for HypE with population size 50 (left) and population size 100 (right) on the lazio\_4 instance.}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.75\columnwidth]{randVsCost_ns4_1_OriginalCost_2000gens.eps}
	\vspace{-1em}
	\caption{\label{fig:randVsCostOriginal} Comparison between the random initialization ($\circ$) and the cost-optimal one ($\times$). Shown are the non-dominated solutions in the final populations of 10 independent HypE runs with population size 50 after 2000 generations for all three objectives (top left) and each combination of two objectives on the lazio\_4\_1 instance.}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.75\columnwidth]{randVsCost_ns4_1_New_2000gens.eps}
	\vspace{-1em}
	\caption{\label{fig:randVsCostNew} Comparison between the random initialization ($\circ$) and the cost-optimal one ($\times$). Shown are the non-dominated solutions in the final populations of 10 independent HypE runs with population size 50 after 2000 generations on the uncorrelated\_4 instance.}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.48\columnwidth]{initBoxPlots_OriginalCosts.eps}
	\hfill
	\includegraphics[width=0.48\columnwidth]{initBoxPlots_New.eps}
	\vspace{-1em}
	\caption{\label{fig:costVsRandBoxPlots} Comparison between the random initialization and the cost-optimal one.
	Shown are boxplots of hypervolume values for HypE with population size 50 on the lazio\_4 instance (left) and on the uncorrelated\_4 instance (right) after both 250 and 2000 generations.}
\end{figure}

@@

\begin{figure}%
	\centering
	\includegraphics[width=0.75\columnwidth]{diffPopsizes}%
	\vspace{-1em}
	\caption{\label{fig:popsizes} Nondominated solutions of 10 independent runs after 100,000 function evaluations for HypE with a population size of 50 ($\times$), 100 ($\circ$), and 200 ($\square$) respectively.}
\end{figure}

\begin{figure}%
	\centering
	\includegraphics[width=0.5\columnwidth]{algoComparison}%
	\caption{\label{fig:algoComparison} Boxplots of the hypervolume values of 10 independent runs after 100,000 function evaluations of HypE with a population size of 25, 50, 100, and 200, as well as for NSGA-II.}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.75\columnwidth]{WHypEVsHypE_ns4_1_OriginalCosts2.eps}
	\vspace{-1em}
	\caption{\label{fig:whype} Comparison between the standard HypE selection ($\circ$) with the one of W-HypE ($\times$) when the weighted hypervolume indicator is only sampled in the gray shaded box $[7\cdot 10^3, 10^4]\times[3\cdot 10^7, 4\cdot 10^7]\times[5\cdot 10^5, 1.1\cdot 10^6]$. Shown are all non-dominated solutions for each algorithm after 10 runs with 4,000 generations and population size 25.}
\end{figure}

@@

\begin{thebibliography}{20}
\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{\texttt{#1}}
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{doi: #1}\else
  \providecommand{\doi}{doi: \begingroup \urlstyle{rm}\Url}\fi

\bibitem[Akgun et~al.(2000)Akgun, Erkut, and Batta]{aeb2000a}
V.~Akgun, E.~Erkut, and R.~Batta.
\newblock {On Finding Dissimilar Paths}.
\newblock \emph{European Journal of Operational Research}, 121\penalty0
  (2):\penalty0 232--246, 2000.
\newblock \doi{10.1016/S0377-2217(99)00214-3}.

\bibitem[Auger et~al.(2009)Auger, Bader, Brockhoff, and Zitzler]{abbz2009b}
A.~Auger, J.~Bader, D.~Brockhoff, and E.~Zitzler.
\newblock {Articulating User Preferences in Many-Objective Problems by Sampling
  the Weighted Hypervolume}.
\newblock In G.~Raidl et~al., editors, \emph{Genetic and Evolutionary
  Computation Conference (GECCO 2009)}, pages 555--562, New York, NY, USA,
  2009. ACM.

\bibitem[Bader and Zitzler(2011)]{bz2011a}
J.~Bader and E.~Zitzler.
\newblock {HypE: An Algorithm for Fast Hypervolume-Based Many-Objective
  Optimization}.
\newblock \emph{Evolutionary Computation}, 19\penalty0 (1):\penalty0 45–--76,
  2011.

\bibitem[Bader et~al.(2011)Bader, Brockhoff, Thiele, and Zitzler]{bbtz2011a}
J.~Bader, D.~Brockhoff, L.~Thiele, and E.~Zitzler.
\newblock {Directed Multiobjective Optimization Based on the Hypervolume
  Indicator}.
\newblock \emph{Journal of Multi-Criteria Decision Analysis}, 2011.
\newblock submitted.

\bibitem[Bianco et~al.(2009)Bianco, Caramia, and Giordani]{bcg2009a}
L.~Bianco, M.~Caramia, and S.~Giordani.
\newblock {A Bilevel Flow Model for Hazmat Transportation Network Design}.
\newblock \emph{Transportation research Part C: Emerging technologies},
  17\penalty0 (2):\penalty0 175--196, 2009.
\newblock \doi{10.1016/j.trc.2008.10.001}.

\bibitem[Bleuler et~al.(2001)Bleuler, Brack, Thiele, and Zitzler]{bbtz2001a}
S.~Bleuler, M.~Brack, L.~Thiele, and E.~Zitzler.
\newblock {Multiobjective Genetic Programming: Reducing Bloat by Using
  {SPEA2}}.
\newblock In \emph{Congress on Evolutionary Computation (CEC~2001)}, pages
  536--543, Piscataway, NJ, 2001. IEEE Press.

\bibitem[Bleuler et~al.(2003)Bleuler, Laumanns, Thiele, and Zitzler]{bltz2003a}
S.~Bleuler, M.~Laumanns, L.~Thiele, and E.~Zitzler.
\newblock {PISA---A Platform and Programming Language Independent Interface for
  Search Algorithms}.
\newblock In C.~M. Fonseca et~al., editors, \emph{Conference on Evolutionary
  Multi-Criterion Optimization {(EMO~2003)}}, volume 2632 of \emph{LNCS}, pages
  494--508, Berlin, 2003. Springer.

\bibitem[Caramia and Dell'Olmo(2008)]{cd2008a}
M.~Caramia and P.~Dell'Olmo.
\newblock \emph{{Multi-objective Management in Freight Logistics: Increasing
  Capacity, Service Level and Safety With Optimization Algorithms}}.
\newblock Springer, 2008.

\bibitem[{Coello Coello} et~al.(2007){Coello Coello}, {Lamont}, and {Van
  Veldhuizen}]{cvl2007a}
C.~A. {Coello Coello}, G.~B. {Lamont}, and D.~A. {Van Veldhuizen}.
\newblock \emph{{Evolutionary Algorithms for Solving Multi-Objective
  Problems}}.
\newblock Springer, Berlin, Germany, 2007.

\bibitem[Deb(2001)]{deb2001a}
K.~Deb.
\newblock \emph{{Multi-Objective Optimization Using Evolutionary Algorithms}}.
\newblock Wiley, Chichester, UK, 2001.

\bibitem[Deb et~al.(2002)Deb, Pratap, Agarwal, and Meyarivan]{dapm2002a}
K.~Deb, A.~Pratap, S.~Agarwal, and T.~Meyarivan.
\newblock {A Fast and Elitist Multiobjective Genetic Algorithm: NSGA-II}.
\newblock \emph{IEEE Transactions on Evolutionary Computation}, 6\penalty0
  (2):\penalty0 182--197, 2002.

\bibitem[Dell'Olmo et~al.(2005)Dell'Olmo, Gentili, and Scozzari]{dgs2005a}
P.~Dell'Olmo, M.~Gentili, and A.~Scozzari.
\newblock {On Finding Dissimilar Pareto-optimal Paths}.
\newblock \emph{European Journal of Operational Research}, 162\penalty0
  (1):\penalty0 70--82, 2005.

\bibitem[Erkut et~al.(2007)Erkut, Tjandra, and Verter]{etv2007a}
E.~Erkut, S.~A. Tjandra, and V.~Verter.
\newblock {Chapter 9: Hazardeous Materials Transportation}.
\newblock In C.~Barnhart and G.~Laporte, editors, \emph{Handbooks in Operations
  Research and Management Science}, volume~14, pages 539--621. Elsevier, 2007.

\bibitem[Goldberg(1989)]{gold1989a}
D.~E. Goldberg.
\newblock \emph{{Genetic Algorithms in Search, Optimization, and Machine
  Learning}}.
\newblock Addison-Wesley, Reading, Massachusetts, 1989.

\bibitem[Gopalan et~al.(1990)Gopalan, Kolluri, Batta, and Karwan]{gkbk1990a}
R.~Gopalan, K.~S. Kolluri, R.~Batta, and M.~H. Karwan.
\newblock {Modeling Equity of Risk in the Transportation of Hazardous
  Materials}.
\newblock \emph{Operations Research}, 38\penalty0 (6):\penalty0 961--975, 1990.

\bibitem[Horoba(2009)]{horo2009a}
C.~Horoba.
\newblock {Analysis of a Simple Evolutionary Algorithm for the Multiobjective
  Shortest Path Problem}.
\newblock In \emph{Foundations of Genetic Algorithms (FOGA 2009)}, pages
  113--120. ACM, 2009.

\bibitem[Wagner et~al.(2007)Wagner, Beume, and Naujoks]{wbn2007a}
T.~Wagner, N.~Beume, and B.~Naujoks.
\newblock {Pareto-\nolinebreak[4], Aggregation\mbox{-}, and Indicator-based
  Methods in Many-objective Optimization}.
\newblock In S.~Obayashi et~al., editors, \emph{Conference on Evolutionary
  Multi-Criterion Optimization (EMO~2007)}, volume 4403 of \emph{LNCS}, pages
  742--756, Berlin Heidelberg, Germany, 2007. Springer.

\bibitem[Zitzler et~al.(2003)Zitzler, Thiele, Laumanns, Fonseca, and {Grunert
  da Fonseca}]{ztlf2003a}
E.~Zitzler, L.~Thiele, M.~Laumanns, C.~M. Fonseca, and V.~{Grunert da Fonseca}.
\newblock {Performance Assessment of Multiobjective Optimizers: An Analysis and
  Review}.
\newblock \emph{IEEE Transactions on Evolutionary Computation}, 7\penalty0
  (2):\penalty0 117--132, 2003.

\bibitem[Zitzler et~al.(2007)Zitzler, Brockhoff, and Thiele]{zbt2007a}
E.~Zitzler, D.~Brockhoff, and L.~Thiele.
\newblock {The Hypervolume Indicator Revisited: On the Design of
  Pareto-compliant Indicators Via Weighted Integration}.
\newblock In S.~Obayashi et~al., editors, \emph{Conference on Evolutionary
  Multi-Criterion Optimization (EMO~2007)}, volume 4403 of \emph{LNCS}, pages
  862--876, Berlin, 2007. Springer.

\bibitem[Zitzler et~al.(2010)Zitzler, Thiele, and Bader]{ztb2010a}
E.~Zitzler, L.~Thiele, and J.~Bader.
\newblock {On Set-Based Multiobjective Optimization}.
\newblock \emph{IEEE Transactions on Evolutionary Computation}, 14\penalty0
  (1):\penalty0 58--79, 2010.

\end{thebibliography}
